### 2012-12-16 inst/examples/reed-example.Rmd
Updated example Ricker approximation vs GP approx to BH

We use the model of

@@

With parameters `r p`.

>>>>

We use a Beverton-Holt model to drive the underlying dynamics, with parameters $A =$ `r p[1]` and $B =$ `r p[2]`.

@@

We consider stochastic growth driven by a lognormal noise process, $X_{t+1} = z_g f(X_t)$, where $f$ is the stock recruitment curve and $z_g$ a lognormal shock with $\sigma_g$ = `r sigma_g`.
